MRD_final_microbiome

### 2019-06-26 import_popln_data.Rmd
updated

setwd("~/globalmicrobiome")
# files nwed to be in the owrking directory
mnd.incidence <- as.data.frame(read_csv("MND-I-B.csv",col_names = TRUE))
mnd.prev <- as.data.frame(read_csv("MND-P-B.csv",col_names = TRUE))
mnd.incidence <- mb.gather(mnd.incidence)
mnd.prev <- mb.gather(mnd.prev)

>>>>

setwd("~/globalmicrobiome")
# files nwed to be in the owrking directory

# For MND
mnd.incidence <- as.data.frame(read_csv("./rawdata/MND-I-B.csv",col_names = TRUE))
mnd.prev <- as.data.frame(read_csv("./rawdata/MND-P-B.csv",col_names = TRUE))

mnd.roc.i <- as.data.frame(read_csv("./rawdata/MND-I-B-RoC.csv",col_names = TRUE))

mnd.roc.p <- as.data.frame(read_csv("./rawdata/MND-P-B-RoC.csv",col_names = TRUE))

# Run function and change name
mnd.incidence <- mb.gather(mnd.incidence)
colnames(mnd.incidence)[2] <- "incidence"

mnd.roc.i <- mb.gather(mnd.roc.i)
colnames(mnd.roc.i)[2] <- "ROC incidence"

mnd.prev <- mb.gather(mnd.prev)
colnames(mnd.prev)[2] <- "prevalance"

mnd.roc.p <- mb.gather(mnd.roc.p)
colnames(mnd.roc.p)[2] <- "ROC prevalance"
# Join them together. 
mnd.ip <- right_join(mnd.prev, mnd.roc.p, by = "Location")
mnd.ip <- right_join(mnd.ip, mnd.incidence, by = "Location")
mnd.ip <- right_join(mnd.ip, mnd.roc.i, by = "Location")

# For IPD

ipd.incidence <- as.data.frame(read_csv("./rawdata/PD-I-B.csv",col_names = TRUE))
ipd.prev <- as.data.frame(read_csv("./rawdata/PD-P-B.csv",col_names = TRUE))

ipd.roc.i <- as.data.frame(read_csv("./rawdata/PD-I-B-RoC.csv",col_names = TRUE))

ipd.roc.p <- as.data.frame(read_csv("./rawdata/PD-P-B-RoC.csv",col_names = TRUE))

# Run function and change name
ipd.incidence <- mb.gather(ipd.incidence)
colnames(ipd.incidence)[2] <- "incidence"

ipd.roc.i <- mb.gather(ipd.roc.i)
colnames(ipd.roc.i)[2] <- "ROC incidence"

ipd.prev <- mb.gather(ipd.prev)
colnames(ipd.prev)[2] <- "prevalance"

ipd.roc.p <- mb.gather(ipd.roc.p)
colnames(ipd.roc.p)[2] <- "ROC prevalance"
# Join them together. 
ipd.ip <- right_join(ipd.prev, ipd.roc.p, by = "Location")
ipd.ip <- right_join(ipd.ip, ipd.incidence, by = "Location")
ipd.ip <- right_join(ipd.ip, ipd.roc.i, by = "Location")

# For AD
ad.incidence <- as.data.frame(read_csv("./rawdata/AD-I-B.csv",col_names = TRUE))
ad.prev <- as.data.frame(read_csv("./rawdata/AD-P-B.csv",col_names = TRUE))

ad.roc.i <- as.data.frame(read_csv("./rawdata/AD-I-B-RoC.csv",col_names = TRUE))

ad.roc.p <- as.data.frame(read_csv("./rawdata/AD-P-B-RoC.csv",col_names = TRUE))

# Run function and change name
ad.incidence <- mb.gather(ad.incidence)
colnames(ad.incidence)[2] <- "incidence"

ad.roc.i <- mb.gather(ad.roc.i)
colnames(ad.roc.i)[2] <- "ROC incidence"

ad.prev <- mb.gather(ad.prev)
colnames(ad.prev)[2] <- "prevalance"

ad.roc.p <- mb.gather(ad.roc.p)
colnames(ad.roc.p)[2] <- "ROC prevalance"
# Join them together. 
ad.ip <- right_join(ad.prev, ad.roc.p, by = "Location")
ad.ip <- right_join(ad.ip, ad.incidence, by = "Location")
ad.ip <- right_join(ad.ip, ad.roc.i, by = "Location")

plot(ad.ip$incidence,ad.ip$prevalance)
plot(ipd.ip$incidence,ipd.ip$prevalance)
plot(mnd.ip$incidence,mnd.ip$prevalance)
